Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-24 Arxiv/main.tex
update theorems

\begin{thm}
 \label{thm_hellinegr_equality_dirichlet}
 In Dirichlet-multinomial system, for 3 different Dirichlet distributions $\dirichlet(\valpha)$, $\dirichlet(\vbeta_1)$ and $\dirichlet(\vbeta_2)$, $\hellinger(\dirichlet(\valpha),\dirichlet(\vbeta_1)) = \hellinger(\dirichlet(\valpha),\dirichlet(\vbeta_2))$ iff:
  $$
  set(\vbeta_1) = set(\vbeta_2)\ and\ set(\valpha + \vbeta_1) = set(\valpha + \vbeta_2).
  $$
 \end{thm}

@@

\begin{thm}
 \label{thm_candidate_divide_dirichlet}
 In Dirichlet-multinomial system with $k$-dimensional Dirichlet distribution, for every $r \in \candidateset$:
 $$
 \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)] 
 = |z|\Big ( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]\Big ),
 $$ 
 and $|z| = \min\{\frac{k!}{a_1! a_2! \cdots a_{k_a}!},\frac{k!}{b_1! b_2! \cdots b_{k_b}!}\}$, where $\sum{a_i} = \sum{b_i} = k$.
 \end{thm}

 \begin{proof} of Theorem \ref{thm_candidate_divide_dirichlet}.
 By 
 \end{proof}

>>>>

\begin{thm}
 \label{thm_hellinegr_equality_dirichlet}
 In Dirichlet-multinomial system, for 3 different Dirichlet distributions $\dirichlet(\valpha)$, $\dirichlet(\vbeta_1)$ and $\dirichlet(\vbeta_2)$, $\hellinger(\dirichlet(\valpha),\dirichlet(\vbeta_1)) = \hellinger(\dirichlet(\valpha),\dirichlet(\vbeta_2))$ iff:
  $$
  set(\vbeta_1) = set(\vbeta_2)\ and\ set(\valpha + \vbeta_1) = set(\valpha + \vbeta_2),
  $$
  where $set(\cdot)$ means we only consider the value of each dimension in the vector without the order.
 \end{thm}

@@

\begin{thm}
 \label{thm_candidate_divide_dirichlet}
 In Dirichlet-multinomial system with $k$-dimensional Dirichlet distribution, for every $r \in \candidateset$:
 $$
 \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)] 
 = |z|\Big ( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]\Big ),
 $$ 
 and $|z| $ can have $\frac{k! k!}{|a_1|! |a_2|! \cdots |a_{k_a}|! \cdot |b_1|! |b_2|! \cdots |b_{k_b}|!}$ possible values, where $\sum{a_i} = \sum{b_i} = k$.
 \end{thm}

 \begin{proof} of Theorem \ref{thm_candidate_divide_dirichlet}.

 Let $\bysinfer(\dataobs) = \dirichlet(\valpha)$, and $\dirichlet(\vbeta)$ be a candidate from $\candidateset$, 
 $a_i$ is the distinct value in $\valpha$ and $b_i$ the same in $\vbeta$, 
 $|a_i|$ denotes the number of values in $\valpha$ having the value$a_i$ and $|b_i|$ the same in $\vbeta$.
 Then, by combination and permutation, there are $\frac{k! k!}{|a_1|! |a_2|! \cdots |a_{k_a}|! \cdot |b_1|! |b_2|! \cdots |b_{k_b}|!}$ possible combination that satisfy the condition in Theorem \ref{thm_hellinegr_equality_dirichlet}.
 \end{proof}
